A significance test in forward stepwise model selection

### 2013-10-11 paper/paper.tex
Normalize columns, don't project variables

% "Title of the paper"
\title{A significance test for forward stepwise model selection}

@@

So far we have left open the question of choosing among the models in
the forward stepwise sequence, i.e. when to stop stepping
forward. Some classical approaches can be posed as optimization
criteria and stop at the step minimizing
\begin{equation}
\begin{aligned}
\label{eq:subsetregress}
\frac{1}{2} \| y - X \beta_s \|_2^2 + \lambda \pen(\beta_s)
\end{aligned}
\end{equation}
where we have written $\{ \beta_s : s = 1, \ldots, max.steps \}$ as
the sequence of models outputted by forward stepwise. The function
$\pen(\beta)$ is a penalty on model complexity usually taken to be the
number of nonzero entries of $\beta$. Proposals for $\lambda$ include
2 ($C_p$, AIC \todo{cite}), $\log(n)$ (BIC of \cite{BIC}), and
$2\log(p)$ (RIC of \cite{RIC}). In the current paper we provide
accurate p-values when adding the first noise variable group in the forward
stepwise sequence, and it is natural to consider using these p-values
to choose a model. \cite{sequential:fdr} examined some stopping rules
using the asymptotic p-values of \cite{significance:lasso} and showed
their stopping rules control false discovery rate--the expected
proportion of noise variables among variables declared significant
\citep{fdr}. We explore this further in Section \ref{sec:simulations}.

@@

Writing $\hat
\beta(\lambda)$, the solution for a fixed value of $\lambda$, we need
the following facts (ref Tibs2012)

@@

  \item The \emph{active set} $A_k$ is a set of indices of variables
    for which the corresponding coordinates of $\hat \beta(\lambda_k)$
    are potentially nonzero. Any variable with index not in $A_k$ has
    a zero coefficient in $\hat \beta(\lambda_k)$, but the converse is
    not true.

@@

Lockhart et al. prove that, under the null hypothesis that $A_k$
contains all the strong predictor variables, the distribution of a
test statistic $T_k \propto \lambda_k(\lambda_k - \lambda_{k+1})$ is
asymptotically Exp(1). In the lasso case we know a lot about the knots
and active set, but the group lasso picture is slightly more
complicated. For the group lasso, $\hat \beta(\lambda)$ does not have
piecewise linear components. To overcome this difficulty we will
restrict our attention to the first group of variables to enter the
active set since the analysis then follows almost exactly as for the
lasso. (\todo Change this if I can find $\lambda_k$).

>>>>

% "Title of the paper"
\title{A significance test in forward stepwise model selection}

@@

So far we have left open the question of choosing among the models in
the forward stepwise sequence, i.e. when to stop stepping
forward. Some classical approaches can be posed as optimization
criteria and stop at the step minimizing
\begin{equation}
\begin{aligned}
\label{eq:subsetregress}
\frac{1}{2} \| y - X \beta_s \|_2^2 + \lambda \pen(\beta_s)
\end{aligned}
\end{equation}
where we have written $\{ \beta_s : s = 1, \ldots, max.steps \}$ as
the sequence of models outputted by forward stepwise. The function
$\pen(\beta)$ is a penalty on model complexity usually taken to be the
number of nonzero entries of $\beta$. Proposals for $\lambda$ include
2 ($C_p$ of \cite{CP}, AIC of \cite{AIC}), $\log(n)$ (BIC of \cite{BIC}), and
$2\log(p)$ (RIC of \cite{RIC}). In the current paper we provide
accurate p-values when adding the first noise variable group in the forward
stepwise sequence, and it is natural to consider using these p-values
to choose a model. \cite{sequential:fdr} examined some stopping rules
using the asymptotic p-values of \cite{significance:lasso} and showed
their stopping rules control false discovery rate--the expected
proportion of noise variables among variables declared significant
\citep{fdr}. We explore this further in Section \ref{sec:simulations}.

@@

Writing $\hat \beta(\lambda)$ for the lasso solution for a fixed value of $\lambda$, we need
the following facts summarized in \cite{significance:lasso} (ref Tibs2012?).

@@

  \item The \emph{active set} $A_k$ is a set of indices of variables
    for which the corresponding coordinates of $\hat \beta(\lambda_k)$
    are potentially nonzero. Any variable with index not in $A_k$ has
    a zero coefficient in $\hat \beta(\lambda_k)$, but the converse is
    not true. \todo{is this equicorrelation set?}

@@

\cite{significance:lasso} prove that under the null hypothesis that $A_k$
contains all the strong predictor variables, the distribution of a
test statistic $T_k \propto \lambda_k(\lambda_k - \lambda_{k+1})$ is
asymptotically Exp(1). In the lasso case we know a lot about the knots
and active set, but the group lasso picture is slightly more
complicated. For the group lasso, $\hat \beta(\lambda)$ does not have
piecewise linear components. To overcome this difficulty we will
restrict our attention to the first group of variables to enter the
active set since the analysis then follows almost exactly as for the
lasso. (\todo Change this if I can find $\lambda_k$).
